Manuscript_Github_Pchabaudi_pir

### 2021-03-22 Manuscript_pirAnalysis_Github/Pchabaudi24h/Manuscript_Github_Pchabaudi_pir.Rmd
Split chabaudi TPM calculation into new file and started removing SBP

---
title: "Manuscript_Github_Pchabaudi_pir"
author: "Timothy Little"
date: "12/03/2021"
output: html_document
---

@@

```{r read_tpm_rescaled_data}

chab_count_table <- read_xlsx('Manuscript_Frontiers_chabaudi_24h_counts.xlsx')

twentyfour_ct_comb <- tpm(chab_count_table, 
                          lengths = chabaudi_transcript_lengths)

#Setting twentyfour_tpm_ct core dataset - remove pseudogene and re-scaled

twentyfour_tpm_nopseudo <- twentyfour_ct_comb %>% 
  filter(!Geneid %in% 'PCHAS_0420800')

twentyfour_tpm_rescale_nopseudo <- lapply(colnames(twentyfour_tpm_nopseudo), 
                                          function(column_name){
                                            column <- getElement(twentyfour_tpm_nopseudo, 
                                                                 paste(column_name))
                                            if(is.numeric(column)){
                                              #is.numeric to avoid trying to scale the Geneid column
                                              tpm_scale_factor <- 1e6 / sum(column)
                                              tpm_scaled <- as.numeric(column*tpm_scale_factor)
                                            }else{
                                              tpm_scaled <- column
                                            }
                                            return(tpm_scaled)
                                          }) %>% 
  bind_cols

colnames(twentyfour_tpm_rescale_nopseudo) <- colnames(twentyfour_tpm_nopseudo)
# apply(twentyfour_tpm_rescale_nopseudo[,-1], 2, sum)

#Setting the re-scaled version as the default from now on
#Setting twentyfour_tpm_ct core dataset - removed pseudogene and re-scaled
twentyfour_ct_comb <- twentyfour_tpm_rescale_nopseudo

twentyfour_rMT <- select(twentyfour_ct_comb, 
                         matches('Geneid|rMT')) %>% 
  rename_with(~ str_extract(.x,pattern = '(?<=rMT_).+'),
              matches('rMT'))

twentyfour_rMT_avg <- melt(twentyfour_rMT, 
                           variable.name = 'sample',
                           value.name = 'tpm') %>% 
  mutate(stage = str_extract(sample, pattern = '.+(?=_[[:digit:]])')) %>% 
  group_by(Geneid, stage) %>% 
  summarise(mean_tpm = mean(tpm)) %>% 
  dcast(Geneid ~ stage)

twentyfour_SBP <- select(twentyfour_ct_comb, 
                         matches('Geneid|SBP')) %>% 
  rename_with(~ str_extract(.x,pattern = '(?<=SBP_).+'),
              matches('SBP'))

twentyfour_SBP_avg <- melt(twentyfour_SBP, 
                           variable.name = 'sample',
                           value.name = 'tpm') %>% 
  mutate(stage = str_extract(sample, pattern = '.+(?=_[[:digit:]])')) %>% 
  group_by(Geneid, stage) %>% 
  summarise(mean_tpm = mean(tpm)) %>% 
  dcast(Geneid ~ stage)

twentyfour_avgtpm <- list(
  'rMT' = list(
    tpm = twentyfour_rMT_avg,
    experiment = 'rMT'
  ),
  'SBP' = list(
    tpm = twentyfour_SBP_avg,
    experiment = 'SBP'
  )
)

@@

## Figure 3c and Supp figure 3 - Highest expressed all _pir_ heatmap

>>>>

---
title: "Manuscript_Github_Pchabaudi_pir"
author: "Timothy Little"
date: "22/03/2021"
output: html_document
---

@@

@@

## Figure 3c - Highest expressed all _pir_ heatmap
